Co-citations in context

### 2019-06-14 cocit_r.tex
minor

The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process. We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification. Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network. In particular, when using the unconstrained model, highly cited papers were most likely to be
in the HNHC category but this trend does not consistently hold when using the constrained model. Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}). Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.

More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles and may be the consequence of using a random model that has a poor fit to the observed data. On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice. Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.

Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns. Further work might explore additional constraints on random assignment of citations to publications. For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} when defining probabilities for citation substitutions. Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.

>>>>

The principal difference between the two models is a single parameter--the set of references that can be used as substituents during the substitution process. We provided several lines of evidence that showed that changing this one parameter from a global network to the local disciplinary network reduces model misspecification. Furthermore,  using the constrained model (which allows substitutions only within the local network)  instead of the unconstrained model (which allows substitutions in the entire WoS network) produces different trends in terms of conventionality and novelty, depending on the network. In particular, when using the unconstrained model, highly cited papers were most likely to be
in the HNHC category but this trend does not consistently hold when using the constrained model. Instead, we find that conventionality flavored with novelty is {\em not} generally a feature of impactful research. Further,  high ``novelty" is not always indicative of impactful research (as reflected in citation counts), as shown by both Immunology and Metabolism having their highest hit rates for low novelty (Figure \ref{fig:Fig2}). 
%\textcolor{blue}{Of relevance, we found the category displaying the highest hit rate to be sensitive to the study parameters, which include the percentage of articles classified as hits, the z-score percentile threshold that delineates LN and HN, and the publication year.}

More generally, these results show that the trends approaching universality in highly cited papers are not robust to changes in thresholds for defining high impact or high novelty articles, or with time, and may be the consequence of using a random model that has a poor fit to the observed data. On the other hand, while  the constrained model reduces model misspecification compared to the unconstrained model, this does not imply that the constrained model is reasonable nor that trends observed under the constrained model convincingly explain scientific practice. Indeed, there are significant  challenges in using random models to understand human behavior, of which citation practice is one example.

Our work has shown that the use of local networks enables simulations that are more consistent with research citation patterns. Further work might explore additional constraints on random assignment of citations to publications to better align benchmarks with citation practice. For example, the proximity of possible citations as defined in a co-author network~\citep{wallace_lariviere_gingras_2012} might be considered when defining probabilities for citation substitutions. Thus, evaluation in context~\citep{hicks_bibliometrics:_2015} and increased consideration of the disciplinary nature of the scientific enterprise is likely to result in improved models that yield further insight.
